\large{\bf Looking forwards and backwards through locally regulated populations }

### 2022-05-02 forwards-and-backwards.tex
Update on Overleaf.

\documentclass[12pt]{article}
\usepackage{fullpage}
\usepackage{amssymb}
\usepackage{graphics} 
\usepackage{amsmath}
\usepackage[color=yellow]{todonotes}
\usepackage{url}

\usepackage{xcolor}
\usepackage{longtable}
\usepackage[hidelinks]{hyperref}
\usepackage{bbm}

@@

We now prove Equation \eqref{eq: r-gamma comparison square term}. Applying Jensen's inequality, we have
&\left\{
            \rho_r * \eta(y)
            -
            \rho_r * \eta(x)
\right\}^2  \\
&\qquad
=
\left\{
\int
    \left(
        \rho_r(y-w)
        -
        \rho_r(x-w)
\eta(dw)
\right\}^2  \\
&\qquad
=
\left\{
\int
    \left(
        \frac{\rho_r(y-w)}{\rho_r(x-w)}
        -
        1
    \rho_r(x-w)
\eta(dw)
\right\}^2  \\
&\qquad
=
\left(\rho_r * \eta(x)\right)^2 \left\{
\int
    \left(
        \frac{\rho_r(y-w)}{\rho_r(x-w)}
        -
        1
    \frac{\rho_r(x-w)}{\rho_r * \eta(x)}
\eta(dw)
\right\}^2  \\
&\qquad
\le
\left(\rho_r * \eta(x)\right)^2 
\int
    \left(
        \frac{\rho_r(y-w)}{\rho_r(x-w)}
        -
        1
    \frac{\rho_r(x-w)}{\rho_r * \eta(x)}
\eta(dw) \\
&\qquad
=
\rho_r * \eta(x)
\int
    \left(
        \frac{\rho_r(y-w)}{\rho_r(x-w)}
        -
        1
    \rho_r(x-w)
\eta(dw).
Note that since $\epsilon_{\gamma}>\epsilon_{r}$,
    \label{eq: gamma-r convolution comparison}
 \rho_r * \eta(x)=& \int p_{\epsilon^2_r}(x-w) \eta(dw)\\
                 =&  \int \frac{p_{\epsilon^2_r}(x-w)}{p_{\epsilon^2_\gamma}(x-w)}
                  p_{\epsilon^2_\gamma}(x-w) \eta(dw)\\
            \leq & \int \epsilon_\gamma^d \epsilon_r^{-d}
                   e^{-(x-w)^2(\frac{1}{\epsilon^2_r}-\frac{1}{\epsilon^2_\gamma})}
                   p_{\epsilon^2_\gamma}(x-w) \eta(dw)\\
            \leq & \epsilon_\gamma^d \epsilon_r^{-d}\rho_\gamma * \eta(x),
it suffices to show that 
 \theta H_{\theta}(x,w)\rho_r(x-w)\leq \rho_{\gamma}(x-w),
$$H_{\theta}(x,w)=\int_{\mathbb{R}^d}
    \left(
        \frac{\rho_r(y-w)}{\rho_r(x-w)}
        -
        1
q_{\theta}(x,dy).$$
Writing out $H$,
H_\theta(x, w)
=
\int
    \left(
        \exp\left(
            - \frac{1}{2\epsilon_r^2}
            \left\{
                ||y - w||^2 - ||x - w||^2
            \right\}
        -
        1
    \frac{
        e^{-\theta (y - x-\meanq)^{T}\covq^{-1}(y - x-\meanq)  / 2}
    }{
        (2 \pi/ \theta)^{d/2} |\covq|^{1/2}
dy.
Writing $z=y-x-\meanq$, we have that 
||y - w||^2 - ||x - w||^2 
=& ||y||^2-||x||^2 -2\langle y-x, w\rangle \\
=&||x+z+ \meanq||^2-||x||^2-2 \langle z+ \meanq, w\rangle\\
=&2\langle x, z+ \meanq \rangle + ||z+ \meanq||^2-2 \langle z+ \meanq, w\rangle \\
=& 2 \langle x-w, z+ \meanq \rangle + ||z+ \meanq||^2\\
=& 2\langle x-w+ \meanq,\meanq \rangle + 2\langle x-w+ \meanq, z \rangle +||z||^2
As a result, we have 
H_\theta(x, w)
\int
    \left(
        \exp\left(
            - \frac{1}{2\epsilon_r^2}
            \left\{
                2 \langle x-w, z+ \meanq \rangle + ||z+ \meanq||^2
            \right\}
        -
        1
    \frac{
        e^{-\theta z^{T}\covq^{-1}z  / 2}
    }{
        (2 \pi/ \theta)^{d/2} |\covq|^{1/2}
dz\\
=&\exp\left(-\frac{2}{\epsilon_r^2}\langle x-w+ \meanq,\meanq \rangle \right)\\
& \times \int
        \frac{
        \exp\left(
            - \frac{2}{\epsilon_r^2} \langle x-w+ \meanq, z \rangle
            - \frac{1}{\epsilon_r^2} ||z||^2
            e^{-\theta z^{T}\covq^{-1}z  / 2}
    }{
        (2 \pi/ \theta)^{d/2} |\covq|^{1/2}
dz\\ \label{eq: Second moment term matrix calculation}
&-2\exp\left(-\frac{1}{\epsilon_r^2}\langle x-w+ \meanq,\meanq \rangle \right)\\
& \qquad \qquad \times     \int
    \frac{ \exp\left(
             -\frac{1}{\epsilon_r^2}\langle x-w+ \meanq, z \rangle
              -\frac{1}{2\epsilon_r^2} ||z||^2
            \right)e^{-\theta z^{T}\covq^{-1}z  / 2}
        }{
        (2 \pi/ \theta)^{d/2} |\covq|^{1/2} \label{eq: first moment term matrix calculation}
dz\\
&+1.
We now consider the integral of the form 
\int \exp(v^{T}z-C||z||^2) \frac{
        e^{-\theta z^{T}\covq^{-1}z  / 2}
    }{
        (2 \pi/ \theta)^{d/2} |\covq|^{1/2}
dz   
for $v \in \mathbb{R}^d$ and $C>0$. 
We have 
&\int \exp(v^{T}z-C||z||^2) \frac{
        e^{-\theta z^{T}\covq^{-1}z  / 2}
    }{
        (2 \pi/ \theta)^{d/2} |\covq|^{1/2}
dz\\
=&\frac{1}{|\covq|^{1/2}|  |\covq^{-1}(I+2C\covq/\theta )|^{1/2}  }\int \exp(v^{T}z) \frac{
        e^{-\theta z^{T}\covq^{-1}(I+2C\covq/\theta )z  / 2}
    }{
        (2 \pi/ \theta)^{d/2}|\covq^{-1}(I+2C\covq/\theta )|^{-1/2} 
dz\\
=& \frac{1}{|I+2C\covq/\theta |^{1/2}} \mathbb{E}_{Z}[\exp (v^{T}Z)]\\
=&\frac{1}{|I+2C\covq/\theta |^{1/2}}
\exp 
\left(
\frac{1}{2}v^{T}\covq/\theta(I+2C\covq/\theta )^{-1}v
\right),
where $Z \sim N(0, \covq/\theta \times (I+2C\covq/\theta )^{-1})$.

In Equation \eqref{eq: gamma-r convolution comparison}, we have established that 
$\rho_r(x-w) / \rho_\gamma(x-w) = C' \exp(-K (x-w)^2 / 2)$
with $K = \frac{1}{\epsilon_r^2} - \frac{1}{\epsilon_\gamma^2}$.
Therefore it suffices to show that for all $x,w \in \mathbb{R}^d$ and $s \in [0, 1/\theta]$, 
\begin{align} 
    F'(s) \exp\left(-A (x-w)^2 \right) \le C .
\end{align}

Finally note that, 
$$F'(s) \leq G_1'(s)+2G_2'(s),$$
where 
$$A_1= 2\epsilon_r^{-2} \covq, ~ v_1=\epsilon_r^{-2}(w-x-\meanq), ~B_1 = 2\covq, ~C_1=2\epsilon_r^{-2} \covq,$$
and 
$$A_2= 2\epsilon_r^{-2} \covq, ~ v_2=\epsilon_r^{-2}(w-x-\meanq), ~B_2 = \covq/2, ~C_2=2\epsilon_r^{-2} \covq,$$
Substituting these quantities on Equation \eqref{eq: bounds on G} shows that Equation \eqref{eqn:goal3} is satisfied as long as $\epsilon_r < \epsilon_\gamma$.
\end{proof}

@@

\begin{lemma}[Convergence of generators for the population process]
As $\theta \to \infty$,
$(\eta^{\theta}_t)_{t \geq 0}$ converges in $\mathcal{D}_{[0,\infty)}(\mathcal{M}_f(\mathbb{R}^d))$
to $(\eta^{\infty}(t))_{t \geq 0}$.
\end{lemma}
\begin{proof}
We use Theorem 4.8.10 in \cite{EK}.
First of all, the set of functions
$\{F_f(\eta):= F(\langle f, \eta \rangle ),~
F \in \mathcal{C}^{2}(\mathbb{R}), ~
f \in \mathcal{C}_{0}(\mathbb{R}^d)\}$
is a dense and convergence-determining 
subset of functions in $\mathcal{M}_f(\mathbb{R}^d)$.
Therefore, it suffices to show that for any $t>0$,
\begin{equation}
    \label{eq: Convergence Condition}
\lim_{\theta \to \infty}
\mathbb{E}\left[
\left(
F_f(\eta^{\theta}_{t+s})-F_f(\eta^{\theta}_t)
-\int_{t}^{t+s}\Pgen^{\infty}F_f(\eta^{\theta}_s)ds
\right)
\prod_{i=1}^{k}\langle h_i,\eta^{\theta}_{t_i} \rangle
\right]=0
\end{equation}
for all $k\geq 0$, $0\leq t_1<t_2<...,t_k \leq t < t+s$,
and $h_1,...,h_k \in \mathcal{C}_{0}(\mathbb{R}^d)$.

To prove this,
we apply Taylor's series expansion
and make use of the Martingale Problem characterisation
of $\eta^{\theta}_T$.
We have
\begin{equation}
\begin{aligned}
&\mathbb{E}\left[F_f(\eta^{\theta}_{t+s})-F_f(\eta^{\theta}_t)\bigg| \mathcal{F}_t \right]\\
=& F'(\langle f, \eta^{\theta}_t \rangle )
\mathbb{E}\left[
                \langle f, \eta^{\theta}_{t+s}\rangle
                    -\langle f, \eta^{\theta}_t\rangle 
                    \bigg| \mathcal{F}_t
         \right]
+\frac{1}{2}F''(\langle f, \eta^{\theta}_t \rangle )
\mathbb{E}\left[
                \left(
                    \langle f, \eta^{\theta}_{t+s}\rangle -\langle f, \eta^{\theta}_t\rangle
                \right)^2
                \bigg| \mathcal{F}_t
        \right]\\
&+\frac{1}{6}F'''(\langle f, \eta^{\theta}_{t+s'}\rangle)\mathbb{E}\left[
                \left(
                    \langle f, \eta^{\theta}_{t+s}\rangle -\langle f, \eta^{\theta}_t\rangle
                \right)^3
                \bigg| \mathcal{F}_t
        \right]\\
=& F'(\langle f, \eta^{\theta}_t \rangle )\\
& \times  \int_{0}^{t}\bigg\{
        \int\left(   \int \theta
     \left(
        f(z)r\big(z,\rho_{r}*\eta^{\theta}_{s}(z)\big)
            -f(x)r\big(x,\rho_{r}*\eta^{\theta}_{s}(x)\big)
            \right)
                    q_\theta(x,dz)\right)
        \\ & \qquad \qquad \qquad \qquad {} \times
                            \gamma\big(x,\rho_{\gamma}*\eta^{\theta}_{s}(x)\big)
                            \eta^{\theta}_{s}(dx)
     \\ & \qquad \qquad {} +\int 
     f(x)F\big(x,\rho_{F}*\eta^{\theta}_{s}(x)\big)
     \eta^{\theta}_{s}(dx)
    \bigg\} ds\\
&+\frac{1}{2}F''(\langle f, \eta^{\theta}_t \rangle )\\
&\quad \times \frac{\theta}{N} \int_{0}^{t}\bigg\{
\langle \gamma\big(x,\rho_{\gamma}*\eta^{\theta}_{s}(x)\big)
\int f^2(y)r\big(y,\rho_{r}*\eta^{\theta}_{s}(y)\big)q_\theta(x,dy) 
,\eta^{\theta}_{s}(dx)\rangle\\
& \qquad \qquad +\langle \mu\big(x,\eta^{\theta}_{s}\big)f^2(x) 
,\eta^{\theta}_{s}(dx)\rangle \bigg\}ds\\
&+\frac{1}{6}F^{(3)}(\langle f, \eta^{\theta}_{t+s'}\rangle)\mathbb{E}\left[
                \left(
                    \langle f, \eta^{\theta}_{t+s}\rangle -\langle f, \eta^{\theta}_t\rangle
                \right)^3
                \bigg| \mathcal{F}_t
        \right]
\end{aligned}
\end{equation}
for some $s' \in [0,s]$.
\end{proof}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newpage
\section{Technical Lemmas}
\subsection{Proof to Lemma \ref{lem: gamma - r radius comparison}}
    \label{sec: Proof to gamma-r radius comparison}
Suppose that the birth rate at $x$ is
$\gamma(\rho_\gamma * \eta(x))$
and the establishment probability is
$r(\rho_r * \eta(x))$,
for some functions $\gamma$ and $r$,
and where $\rho_\gamma$ and $\rho_r$ are some kernels,
and that the death rate at $x$ is
$$
    \mu(x, \eta) = 
        \gamma(\rho_\gamma * \eta(x))
        r(\rho_r * \eta(x))
        +
        \frac{1}{\theta} F(\rho_R * \eta(x))
$$
for some bounded function $F$ and kernel $\rho_R$ (that is probably either $\rho_r$ or $\rho_\gamma$).

To bound $\IE\left[\langle 1, \eta_t \rangle\right]$
by Gronwall,
we would like to find a bound of the form
\begin{align} \label{eqn:goal}
    \theta \int \left[
        r(\rho_r * \eta(y))
        -
        r(\rho_r * \eta(x))
    \right] q_\theta(x, dy)
    \le
    G( \rho_\gamma * \eta(x) ),
\end{align}
for some polynomial function $G$.

To do this, first we expand $r(\rho_r * \eta(x))$ to second order.
Given $y$, with $x < \tilde y < y$,
\begin{align}
    r(\rho_r * \eta(y)) - r(\rho_r * \eta(x))
    &=
    r'(\rho_r * \eta(x))
    \left\{
        \rho_r * \eta(y)
        -
        \rho_r * \eta(x)
    \right\}
    +
    \frac{1}{2}
    r''(\rho_r * \eta(\tilde y))
    \left\{
        \rho_r * \eta(y)
        -
        \rho_r * \eta(x)
    \right\}^2 .
\end{align}

Putting this in Equation \eqref{eqn:goal}, the second term is then
\begin{align}
&\theta \int
    \frac{1}{2}
    r''(\rho_r * \eta(\tilde y))
    \left\{
        \rho_r * \eta(y)
        -
        \rho_r * \eta(x)
    \right\}^2 
    q_\theta(x, dy)  \\
&\qquad
\le \theta \frac{\|r''\|_\infty}{2}
    \int
    \left\{
        \rho_r * \eta(y)
        -
        \rho_r * \eta(x)
    \right\}^2 
    q_\theta(x, dy)  .
\end{align}

We will first show that this is bounded by a function of $\rho_\gamma * \eta(x)$,
i.e., that for any $x < \tilde y < y$ and $\theta$ sufficiently large,
there is a $C$ with
\begin{align} \label{eqn:goal2}
    \theta \int
    \left\{
        \rho_r * \eta(y)
        -
        \rho_r * \eta(x)
    \right\}^2 
    q_\theta(x, dy)  
\le
C \rho_\gamma * \eta(x) .
\end{align}

Leaving aside the $\frac{\|r''\|_\infty}{2}$ constant,
let's rewrite this so we can use Fubini.
First note that,
since $\rho_r *\eta(x) = \int \rho_r(x - w) \eta(dw)$
is the normalizing constant for the measure proportional to $\rho_r(x - w) \eta(dw)$,
then applying Jensen's inequality,
\begin{align}
&\left\{
            \rho_r * \eta(y)
            -
            \rho_r * \eta(x)
\right\}^2  \\
&\qquad
=
\left\{
\int
    \left(
        \rho_r(y-w)
        -
        \rho_r(x-w)
    \right)
\eta(dw)
\right\}^2  \\
&\qquad
=
\left\{
\int
    \left(
        \frac{\rho_r(y-w)}{\rho_r(x-w)}
        -
        1
    \right)
    \rho_r(x-w)
\eta(dw)
\right\}^2  \\
&\qquad
=
\left(\rho_r * \eta(x)\right)^2 \left\{
\int
    \left(
        \frac{\rho_r(y-w)}{\rho_r(x-w)}
        -
        1
    \right)
    \frac{\rho_r(x-w)}{\rho_r * \eta(x)}
\eta(dw)
\right\}^2  \\
&\qquad
\le
\left(\rho_r * \eta(x)\right)^2 
\int
    \left(
        \frac{\rho_r(y-w)}{\rho_r(x-w)}
        -
        1
    \right)^2
    \frac{\rho_r(x-w)}{\rho_r * \eta(x)}
\eta(dw) \\
&\qquad
=
\rho_r * \eta(x)
\int
    \left(
        \frac{\rho_r(y-w)}{\rho_r(x-w)}
        -
        1
    \right)^2
    \rho_r(x-w)
\eta(dw) .
\end{align}

Now, we don't mind having the $\rho_r * \eta(x)$ term,
so we'd like to bound the remaining bit by $\rho_\gamma * \eta(x)$.
We'll now bring in the integral over $y$ and use Fubini, so that
\begin{align}
&\int \theta
\int
    \left(
        \frac{\rho_r(y-w)}{\rho_r(x-w)}
        -
        1
    \right)^2
    \rho_r(x-w)
\eta(dw)
q_\theta(x, dy) \\
&\qquad
=
\int \theta H_\theta(x, w) \rho_r(x-w) \eta(dw) ,
\end{align}
if we define
\begin{align}
H_\theta(x, w)
:=
\int
    \left(
        \frac{\rho_r(y-w)}{\rho_r(x-w)}
        -
        1
    \right)^2
q_\theta(x, dy) .
\end{align}
So, it only remains to bound $\theta H_\theta (w, x) \rho_r(x-w) $ by $\rho_\gamma(x - w)$.

Now, let's assume that $\rho$ and $q$ are all Gaussian;
to avoid difficulties with notation,
define  $p_t(x) = \exp(-x^2 / 2t) / (2 \pi t)^{d/2}$
to be the heat kernel,
so that $\rho_r(x) = p_{\epsilon_r^2}(x)$
and $q_\theta(x) = p_{1/\theta}(x)$.
Writing out $H$,
\begin{align}
H_\theta(x, w)
=
\int
    \left(
        \exp\left(
            - \frac{1}{2\epsilon_r^2}
            \left\{
                (y - w)^2 - (x - w)^2
            \right\}
        \right)
        -
        1
    \right)^2
    \frac{
        e^{-\theta(y - x)^2 / 2}
    }{
        (2 \pi / \theta)^{d/2}
    }
dy .
\end{align}

We'll just multiply this out and evaluate it directly,
using the fact that
\begin{align}
&
\int e^{-a z - b z^2 / 2} \frac{e^{-\theta z^2 / 2}}{(2 \pi / \theta)^{d/2}} dz
\\ &\qquad
=
\left(
    \frac{ \theta }{ \theta + b }
\right)^{d/2}
\int e^{-a z} \frac{e^{-(\theta + b) z^2 / 2}}{(2 \pi / (\theta + b))^{d/2}} dz
\\ &\qquad
= \label{eqn:mgf}
\left(
    \frac{ \theta }{ \theta + b }
\right)^{d/2}
\exp\left( \frac{ a^2 }{ 2 (\theta + b) } \right) ,
\end{align}
(since $Z \sim \text{Normal}(0, \sigma^2)$ then $\IE[e^{tZ}] = \exp(\sigma^2 t^2 / 2)$).

>>>>

\documentclass[12pt]{article}
\usepackage{fullpage}
\usepackage{amssymb}
\usepackage{graphics} 
\usepackage{amsmath}
\usepackage[color=yellow]{todonotes}
\usepackage{url}
\usepackage{xcolor}
\usepackage{longtable}
\usepackage[hidelinks]{hyperref}
\usepackage{bbm}

@@

We now prove Equation \eqref{eq: r-gamma comparison square term}. Applying Jensen's inequality, we have
\begin{align}
&\left\{
            \rho_r * \eta(y)
            -
            \rho_r * \eta(x)
\right\}^2  \\
&\qquad
=
\left\{
\int
    \left(
        \rho_r(y-w)
        -
        \rho_r(x-w)
    \right)
\eta(dw)
\right\}^2  \\
&\qquad
=
\left\{
\int
    \left(
        \frac{\rho_r(y-w)}{\rho_r(x-w)}
        -
        1
    \right)
    \rho_r(x-w)
\eta(dw)
\right\}^2  \\
&\qquad
=
\left(\rho_r * \eta(x)\right)^2 \left\{
\int
    \left(
        \frac{\rho_r(y-w)}{\rho_r(x-w)}
        -
        1
    \right)
    \frac{\rho_r(x-w)}{\rho_r * \eta(x)}
\eta(dw)
\right\}^2  \\
&\qquad
\le
\left(\rho_r * \eta(x)\right)^2 
\int
    \left(
        \frac{\rho_r(y-w)}{\rho_r(x-w)}
        -
        1
    \right)^2
    \frac{\rho_r(x-w)}{\rho_r * \eta(x)}
\eta(dw) \\
&\qquad
=
\rho_r * \eta(x)
\int
    \left(
        \frac{\rho_r(y-w)}{\rho_r(x-w)}
        -
        1
    \right)^2
    \rho_r(x-w)
\eta(dw).
\end{align}
Note that since $\epsilon_{\gamma}>\epsilon_{r}$,
\begin{equation}
    \label{eq: gamma-r convolution comparison}
\begin{aligned}
 \rho_r * \eta(x)=& \int p_{\epsilon^2_r}(x-w) \eta(dw)\\
                 =&  \int \frac{p_{\epsilon^2_r}(x-w)}{p_{\epsilon^2_\gamma}(x-w)}
                  p_{\epsilon^2_\gamma}(x-w) \eta(dw)\\
            \leq & \int \epsilon_\gamma^d \epsilon_r^{-d}
                   e^{-(x-w)^2(\frac{1}{\epsilon^2_r}-\frac{1}{\epsilon^2_\gamma})}
                   p_{\epsilon^2_\gamma}(x-w) \eta(dw)\\
            \leq & \epsilon_\gamma^d \epsilon_r^{-d}\rho_\gamma * \eta(x),
\end{aligned}
\end{equation}
it suffices to show that 
\begin{equation}\label{eq: gaussian density estimate}
 \theta H_{\theta}(x,w)\rho_r(x-w)\leq \rho_{\gamma}(x-w),
\end{equation}
where
$$H_{\theta}(x,w)=\int_{\mathbb{R}^d}
    \left(
        \frac{\rho_r(y-w)}{\rho_r(x-w)}
        -
        1
    \right)^2
q_{\theta}(x,dy).$$
For the proof of Equation \eqref{eq: gaussian density estimate} refer to the Lemma \ref{eq: Gaussin density estimates} in the Appendix.

@@

\begin{lemma}[Convergence of generators for the population process]
As $\theta \to \infty$,
$(\eta^{\theta}_t)_{t \geq 0}$ converges in $\mathcal{D}_{[0,\infty)}(\mathcal{M}_f(\mathbb{R}^d))$
to $(\eta^{\infty}(t))_{t \geq 0}$.
\end{lemma}
\begin{proof}
We use Theorem 4.8.10 in \cite{EK}.
First of all, the set of functions
$\{F_f(\eta):= F(\langle f, \eta \rangle ),~
F \in \mathcal{C}^{2}(\mathbb{R}), ~
f \in \mathcal{C}_{0}(\mathbb{R}^d)\}$
is a dense and convergence-determining 
subset of functions in $\mathcal{M}_f(\mathbb{R}^d)$.
Therefore, it suffices to show that for any $t>0$,
\begin{equation}
    \label{eq: Convergence Condition}
\lim_{\theta \to \infty}
\mathbb{E}\left[
\left(
F_f(\eta^{\theta}_{t+\tau})-F_f(\eta^{\theta}_t)
-\int_{t}^{t+\tau}\Pgen^{\infty}F_f(\eta^{\theta}_s)ds
\right)
\prod_{i=1}^{k}\langle h_i,\eta^{\theta}_{t_i} \rangle
\right]=0
\end{equation}
for all $k\geq 0$, $0\leq t_1<t_2<...,t_k \leq t < t+\tau$,
and $h_1,...,h_k \in \mathcal{C}_{0}(\mathbb{R}^d)$.

To prove this,
we apply Taylor's series expansion
and make use of the Martingale Problem characterisation
of $\eta^{\theta}_T$.
We have
\begin{equation}
\begin{aligned}
&\mathbb{E}\left[F_f(\eta^{\theta}_{t+\tau})-F_f(\eta^{\theta}_t)\bigg| \mathcal{F}_t \right]\\
=& F'(\langle f, \eta^{\theta}_t \rangle )
\mathbb{E}\left[
                \langle f, \eta^{\theta}_{t+\tau}\rangle
                    -\langle f, \eta^{\theta}_t\rangle 
                    \bigg| \mathcal{F}_t
         \right]
+\frac{1}{2}F''(\langle f, \eta^{\theta}_t \rangle )
\mathbb{E}\left[
                \left(
                    \langle f, \eta^{\theta}_{t+\tau}\rangle -\langle f, \eta^{\theta}_t\rangle
                \right)^2
                \bigg| \mathcal{F}_t
        \right]\\
&+\frac{1}{6}F'''(\langle f, \eta^{\theta}_{t+\tau'}\rangle)\mathbb{E}\left[
                \left(
                    \langle f, \eta^{\theta}_{t+\tau}\rangle -\langle f, \eta^{\theta}_t\rangle
                \right)^3
                \bigg| \mathcal{F}_t
        \right]\\
=& F'(\langle f, \eta^{\theta}_t \rangle )\\
& \times  \int_{t}^{t+\tau}\bigg\{
        \int\left(   \int \theta
     \left(
        f(z)r\big(z,\rho_{r}*\eta^{\theta}_{s}(z)\big)
            -f(x)r\big(x,\rho_{r}*\eta^{\theta}_{s}(x)\big)
            \right)
                    q_\theta(x,dz)\right)
        \\ & \qquad \qquad \qquad \qquad {} \times
                            \gamma\big(x,\rho_{\gamma}*\eta^{\theta}_{s}(x)\big)
                            \eta^{\theta}_{s}(dx)
     \\ & \qquad \qquad {} +\int 
     f(x)F\big(x,\rho_{F}*\eta^{\theta}_{s}(x)\big)
     \eta^{\theta}_{s}(dx)
    \bigg\} ds\\
&+\frac{1}{2}F''(\langle f, \eta^{\theta}_t \rangle )\\
&\quad \times \frac{\theta}{N}\int_{t}^{t+\tau}\bigg\{
\langle \gamma\big(x,\rho_{\gamma}*\eta^{\theta}_{s}(x)\big)
\int f^2(y)r\big(y,\rho_{r}*\eta^{\theta}_{s}(y)\big)q_\theta(x,dy) 
,\eta^{\theta}_{s}(dx)\rangle\\
& \qquad \qquad +\langle \mu\big(x,\eta^{\theta}_{s}\big)f^2(x) 
,\eta^{\theta}_{s}(dx)\rangle \bigg\}ds\\
&+\frac{1}{6}F^{(3)}(\langle f, \eta^{\theta}_{t+\tau'}\rangle)\mathbb{E}\left[
                \left(
                    \langle f, \eta^{\theta}_{t+\tau}\rangle -\langle f, \eta^{\theta}_t\rangle
                \right)^3
                \bigg| \mathcal{F}_t
        \right]
\end{aligned}
\end{equation}
for some $s' \in [0,s]$.

We first show that 
$$\lim_{\theta \to \infty}\mathbb{E}\left[
                \left|
                    \langle f, \eta^{\theta}_{t+\tau}\rangle -\langle f, \eta^{\theta}_t\rangle
                \right|^3
                \bigg| \mathcal{F}_t
        \right] \to 0.$$
Since the total number of births and deaths
between $[t,t+\tau]$ is given by Poisson point processes
with rates $\theta \gamma\big(x,\rho_{\gamma}*\eta^{\theta}_{s}(x)\big)$
and $\theta \mu\big(x,\eta^{\theta}_{s}\big)$
respectively,
and each birth and death events contribute
an increment of order $\mathcal{O}(1/N^3)$,
we have that
\begin{multline}
\lim_{\theta \to \infty}\mathbb{E}\left[
                \left|
                    \langle f, \eta^{\theta}_{t+\tau}\rangle -\langle f, \eta^{\theta}_t\rangle
                \right|^3
                \bigg| \mathcal{F}_t
        \right] \\
\leq ||f||_{\theta} \frac{\theta}{N^2}\int_{0}^{t}\left\langle\gamma\big(x,\rho_{\gamma}*\eta^{\theta}_{s}(x)\big)+\mu\big(x,\eta^{\theta}_{s}\big), \eta^{\theta}_s(dx)\right\rangle ds \to 0
\end{multline}
as $\theta \to \infty$.
\end{proof}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage

\section{Technical Lemmas}
\subsection{Gaussian Kernel Estimates}

\begin{lemma}\label{eq: Gaussin density estimates}
\begin{equation}\label{eq: gaussian density estimate}
 \theta H_{\theta}(x,w)\rho_r(x-w)\leq \rho_{\gamma}(x-w),
\end{equation}
where
$$H_{\theta}(x,w)=\int_{\mathbb{R}^d}
    \left(
        \frac{\rho_r(y-w)}{\rho_r(x-w)}
        -
        1
    \right)^2
q_{\theta}(x,dy).$$
\end{lemma}
\begin{proof}

Writing out $H$,
\begin{align}
H_\theta(x, w)
=
\int
    \left(
        \exp\left(
            - \frac{1}{2\epsilon_r^2}
            \left\{
                ||y - w||^2 - ||x - w||^2
            \right\}
        \right)
        -
        1
    \right)^2
    \frac{
        e^{-\theta (y - x-\meanq)^{T}\covq^{-1}(y - x-\meanq)  / 2}
    }{
        (2 \pi/ \theta)^{d/2} |\covq|^{1/2}
    }
dy.
\end{align}
Writing $z=y-x-\meanq$, we have that 
\begin{equation}
\begin{aligned}
||y - w||^2 - ||x - w||^2 
=& ||y||^2-||x||^2 -2\langle y-x, w\rangle \\
=&||x+z+ \meanq||^2-||x||^2-2 \langle z+ \meanq, w\rangle\\
=&2\langle x, z+ \meanq \rangle + ||z+ \meanq||^2-2 \langle z+ \meanq, w\rangle \\
=& 2 \langle x-w, z+ \meanq \rangle + ||z+ \meanq||^2\\
=& 2\langle x-w+ \meanq,\meanq \rangle + 2\langle x-w+ \meanq, z \rangle +||z||^2
\end{aligned}
\end{equation}
As a result, we have 
\begin{align}
H_\theta(x, w)
=&
\int
    \left(
        \exp\left(
            - \frac{1}{2\epsilon_r^2}
            \left\{
                2 \langle x-w, z+ \meanq \rangle + ||z+ \meanq||^2
            \right\}
        \right)
        -
        1
    \right)^2
    \frac{
        e^{-\theta z^{T}\covq^{-1}z  / 2}
    }{
        (2 \pi/ \theta)^{d/2} |\covq|^{1/2}
    }
dz\\
=&\exp\left(-\frac{2}{\epsilon_r^2}\langle x-w+ \meanq,\meanq \rangle \right)\\
& \times \int
        \frac{
        \exp\left(
            - \frac{2}{\epsilon_r^2} \langle x-w+ \meanq, z \rangle
            - \frac{1}{\epsilon_r^2} ||z||^2
            \right)
            e^{-\theta z^{T}\covq^{-1}z  / 2}
    }{
        (2 \pi/ \theta)^{d/2} |\covq|^{1/2}
    }
dz\\ \label{eq: Second moment term matrix calculation}
&-2\exp\left(-\frac{1}{\epsilon_r^2}\langle x-w+ \meanq,\meanq \rangle \right)\\
& \qquad \qquad \times     \int
    \frac{ \exp\left(
             -\frac{1}{\epsilon_r^2}\langle x-w+ \meanq, z \rangle
              -\frac{1}{2\epsilon_r^2} ||z||^2
            \right)e^{-\theta z^{T}\covq^{-1}z  / 2}
        }{
        (2 \pi/ \theta)^{d/2} |\covq|^{1/2} \label{eq: first moment term matrix calculation}
    }
dz\\
&+1.
\end{align}
We now consider the integral of the form 
\begin{equation}
\int \exp(v^{T}z-C||z||^2) \frac{
        e^{-\theta z^{T}\covq^{-1}z  / 2}
    }{
        (2 \pi/ \theta)^{d/2} |\covq|^{1/2}
    }
dz   
\end{equation}
for $v \in \mathbb{R}^d$ and $C>0$. 
We have 
\begin{equation}
\begin{aligned}
&\int \exp(v^{T}z-C||z||^2) \frac{
        e^{-\theta z^{T}\covq^{-1}z  / 2}
    }{
        (2 \pi/ \theta)^{d/2} |\covq|^{1/2}
    }
dz\\
=&\frac{1}{|\covq|^{1/2}|  |\covq^{-1}(I+2C\covq/\theta )|^{1/2}  }\int \exp(v^{T}z) \frac{
        e^{-\theta z^{T}\covq^{-1}(I+2C\covq/\theta )z  / 2}
    }{
        (2 \pi/ \theta)^{d/2}|\covq^{-1}(I+2C\covq/\theta )|^{-1/2} 
    }
dz\\
=& \frac{1}{|I+2C\covq/\theta |^{1/2}} \mathbb{E}_{Z}[\exp (v^{T}Z)]\\
=&\frac{1}{|I+2C\covq/\theta |^{1/2}}
\exp 
\left(
\frac{1}{2}v^{T}\covq/\theta(I+2C\covq/\theta )^{-1}v
\right),
\end{aligned}
\end{equation}
where $Z \sim N(0, \covq/\theta \times (I+2C\covq/\theta )^{-1})$.

In Equation \eqref{eq: gamma-r convolution comparison}, we have established that 
$\rho_r(x-w) / \rho_\gamma(x-w) = C' \exp(-K (x-w)^2 / 2)$
with $K = \frac{1}{\epsilon_r^2} - \frac{1}{\epsilon_\gamma^2}$.
Therefore it suffices to show that for all $x,w \in \mathbb{R}^d$ and $s \in [0, 1/\theta]$, 
\begin{align}\label{eqn:goal3}
    F'(s) \exp\left(-A (x-w)^2 \right) \le C .
\end{align}

Finally note that, 
$$F'(s) \leq G_1'(s)+2G_2'(s),$$
where 
$$A_1= 2\epsilon_r^{-2} \covq, ~ v_1=\epsilon_r^{-2}(w-x-\meanq), ~B_1 = 2\covq, ~C_1=2\epsilon_r^{-2} \covq,$$
and 
$$A_2= 2\epsilon_r^{-2} \covq, ~ v_2=\epsilon_r^{-2}(w-x-\meanq), ~B_2 = \covq/2, ~C_2=2\epsilon_r^{-2} \covq,$$
Substituting these quantities on Equation \eqref{eq: bounds on G} shows that Equation \eqref{eqn:goal3} is satisfied as long as $\epsilon_r < \epsilon_\gamma$.
